Commutative character sheaves and geometric types for supercuspidal representations

### 2020-07-24 Geometric types.tex
Working on intro

@@

\begin{proof}
By the definition of $\Delta_G$, we have a short exact sequence
\[
1 \to G\der(k) \to G(k) \to G\ab(k) \to \Delta_G \to 1.
\]
Applying $\Hom(-, \EEx)$ yields the bottom row in the statement.

@@

\bib{howe:73a}{article}{
   author={Howe, Roger E.},
   title={On the character of Weil's representation},
   journal={Trans. Amer. Math. Soc.},
   volume={177},
   date={1973},
   pages={287--298},
}

>>>>

Yu's construction has been revisited recently by several authors.
Hakim \cite{hakim:18a}*{\S 2.1} gives an alternate construction beginning with a
representation of a compact-mod-center subgroup of $G$.
Unfortunately, this ingredient does not lend itself to geometrization using our techniques.
In contrast, Kaletha \cite{kaletha:19a} has given a construction in terms of a
tame elliptic maximal torus $S \subset G$ and a character $\theta$ of $S$.
The pair $(S, \theta)$ can already be geometrized using \cite{cunningham-roe:13a} since $S$ is commutative.
However, Kaletha's construction only produces a subset of Yu's supercuspidal representations \cite{kaletha:19a}*{Prop. 3.7.14}, so we phrase our geometrization in terms of Yu's original construction.

@@

\begin{proof}
By the definition of $\Delta_G$, we have a short exact sequence
\[
1 \to G\der(k) \to G(k) \to G\ab(k) \to \Delta_G \to 1.
\]
Applying $\Hom(-, \EEx)$, which is exact since $\EEx$ is divisible, yields the bottom row in the statement.

@@

\bib{hakim:18a}{article}{
author={Hakim, Jeffrey},
title={Constructing tame supercuspidal representations},
journal={Representation Theory},
volume={22},
date={2018},
pages={45--86}
}

\bib{howe:73a}{article}{
   author={Howe, Roger E.},
   title={{On the character of Weil's representation}},
   journal={Trans. Amer. Math. Soc.},
   volume={177},
   date={1973},
   pages={287--298},
}

\bib{kaletha:19a}{article}{
author={Kaletha, Tasho},
title={Regular supercuspidal representations},
journal={J. Amer. Math. Soc.},
volume={32},
date={2019},
pages={1071--1170},
}
